---
title: "SEM with lavaan"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

IMPORTANT: You can delete everything in here and start fresh. You might want to start by not deleting anything above this line until you know what that stuff is doing.


This is an .Rmd file. It is plain text with special features. Any time you write just like this, it will be compiled to normal text in the website. If you put a \# in front of your text, it will create a top level-header.

# 

Last compiled: `r Sys.Date()`

# Path analysis
## การวิเคราะห์เส้นทางอิทธิพล

ตัวอย่างจากบทความวิจัย

```{r}
library(lavaan)
#correalation from article
regression.cor <- lav_matrix_lower2full(c(1.0,
                                          0.14, 1.0,
                                          0.34, -0.14, 1.0,
                                          0.23, -0.03, 0.43, 1.0))
                                          
colnames(regression.cor) <- rownames(regression.cor) <- c("TFL", "TSL", "CTE","TEF")
regression.cor

#model syntax
regression.model <- '
TEF ~ TFL + TSL + CTE
CTE ~ TFL + TSL
'
#model fit
regression.fit <- sem(regression.model, sample.cov = regression.cor, sample.nobs = 813)
summary(regression.fit, rsquare = TRUE)

#diagram
library(semPlot)
semPaths(regression.fit,
         whatLabels="STDE",
         layout = "tree")
#adjust path
semPaths(regression.fit,
         whatLabels="STDE",
         layout = "tree",
         style = "ram",
         rotation = 1,
         sizeMan = 7,
         sizeLat = 7,
         color = "lightgray",
         edge.label.cex = 1.2,
         label.cex = 1.3
         )
```


# Structural Equation Model

ใช้ตัวอย่างจากบทความวิชาการของ     [Download](https://drive.google.com/file/d/1XlNeCyZpZDvq8goRQeYWgELrO_QT2Cw7/view)

ข้อมูลที่ใช้ในการวิเคราะห์ : correlation matrix จากบทความข้างต้น

```{r}
library(lavaan)

lower = '
1.000 
0.859 1.000 
0.873 0.882 1.000
0.816 0.854 0.852 1.000
0.281 0.319 0.297 0.301 1 
0.369 0.363 0.343 0.363 0.628 1

 '
au.cor = getCov(lower, names = c("sa", "rt", "bp","imp", "ao", "we"))
au.cor

au.cov = cor2cov(R = au.cor, sds = c(0.629, 0.341, 0.560, 
                                         0.318,0.284, 0.291 ))
au.cov


model = '
	 	   auf =~ sa + rt + bp + imp
	     aof =~ ao
	     wef =~ we
	     wef~ aof + auf
	     aof ~ auf
	     ao ~~ .01*ao
	     we ~~ .01*we
	     sa ~~ bp
 	 '
#summary(onefactor)
results = sem(model, sample.cov=au.cov, sample.nobs=605)
summary(results, standardize=TRUE, fit.measures=TRUE)
modificationIndices(results, minimum.value = 0)

library(semPlot)

semPaths(results,
         whatLabels = "std",
         layout = "tree")

sessionInfo()

```


