---
title: "Path Analysis"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

IMPORTANT: You can delete everything in here and start fresh. You might want to start by not deleting anything above this line until you know what that stuff is doing.


This is an .Rmd file. It is plain text with special features. Any time you write just like this, it will be compiled to normal text in the website. If you put a \# in front of your text, it will create a top level-header.

# 

Last compiled: `r Sys.Date()`



# Adding R stuff

Last compiled: `r Sys.Date()`

I'm writing this tutorial going from the top down. And, this is how it will be printed. So, notice the second post is second in the list. If you want your most recent post to be at the top, then make a new post starting at the top. If you want the oldest first, do, then keep adding to the bottom

# Adding R stuff

เราใช้ตัวอย่างจากบทความวิชาการของ

Example 1 : [Download](https://drive.google.com/file/d/1XlNeCyZpZDvq8goRQeYWgELrO_QT2Cw7/view)
```{r}
library(lavaan)

lower = '
1.000 
0.859 1.000 
0.873 0.882 1.000
0.816 0.854 0.852 1.000
0.281 0.319 0.297 0.301 1 
0.369 0.363 0.343 0.363 0.628 1

 '
au.cor = getCov(lower, names = c("sa", "rt", "bp","imp", "ao", "we"))
au.cor

au.cov = cor2cov(R = au.cor, sds = c(0.629, 0.341, 0.560, 
                                         0.318,0.284, 0.291 ))
au.cov


model = '
	 	   auf =~ sa + rt + bp + imp
	     aof =~ ao
	     wef =~ we
	     wef~ aof + auf
	     aof ~ auf
	     ao ~~ .01*ao
	     we ~~ .01*we
	     sa ~~ bp
 	 '
#summary(onefactor)
results = sem(model, sample.cov=au.cov, sample.nobs=605)
summary(results, standardize=TRUE, fit.measures=TRUE)
modificationIndices(results, minimum.value = 0)

library(semPlot)

semPaths(results,
         whatLabels = "std",
         layout = "tree")

sessionInfo()

```


