---
title: "SEM with lavaan"
output:
  html_document: 
    toc: yes
    toc_float: yes
    collapsed: no
    toc_depth: 1
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```
```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
```





Last compiled: `r Sys.Date()`
# Basic R

ตรวจสอบตำแหน่ง
```{r}
getwd()
```


# Path analysis

Reading assignment : Kurt, T., Duyar, I., & Calik, T. (2012). Are we legitimate yet? A closer look at the casual relationship mechanisms among principal leadership, teacher self‐efficacy and collective efficacy. Journal of Management Development, 31, 71-86. 

- Data in .txt format [Download](https://github.com/trsamp/SEM101/blob/main/data/01PA.txt)
- Data in SPSS format [Download](https://github.com/trsamp/SEM101/blob/main/data/01PA.sav)

```{r}
library(lavaan)
#correlation from article
regression.cor <- lav_matrix_lower2full(c(1.0,
                                          0.14, 1.0,
                                          0.34, -0.14, 1.0,
                                          0.23, -0.03, 0.43, 1.0))
                                          
colnames(regression.cor) <- rownames(regression.cor) <- c("TFL", "TSL", "CTE","TEF")
regression.cor

reg.cov = cor2cov(R = regression.cor, sds = c(0.82, 0.55, 0.65, 0.99 ))
reg.cov

#model syntax
regression.model <- '
TEF ~ TFL + TSL + CTE
CTE ~ TFL + TSL
'
#model fit
regression.fit <- sem(regression.model, sample.cov = regression.cor, sample.nobs = 813)
summary(regression.fit, standardized = TRUE, rsquare = TRUE)

#diagram
library(semPlot)
semPaths(regression.fit,
         whatLabels="STDE",
         layout = "tree",
         rotation = 1)
#adjust path
semPaths(regression.fit,
         whatLabels="STDE",
         layout = "tree",
         style = "ram",
         rotation = 1,
         sizeMan = 7,
         sizeLat = 7,
         color = "lightgray",
         edge.label.cex = 1.2,
         label.cex = 1.3
         )
```

# Confirmatory Factor Analysis

Reading assignment : Kulophas, D., Hallinger, P., Ruengtrakul, A., & Wongwanich, S. (2018). Exploring the effects of authentic leadership on academic optimism and teacher engagement in Thailand. International Journal of Educational Management, 32(1), 27-45. https://doi.org/10.1108/IJEM-10-2016-0233

- Data in SPSS format [Download](https://github.com/trsamp/SEM101/blob/main/data/03SEM.sav)

```{r}
library(lavaan)

lower = '
1.000 
0.859 1.000 
0.873 0.882 1.000
0.816 0.854 0.852 1.000
0.281 0.319 0.297 0.301 1.000
0.369 0.363 0.343 0.363 0.628 1.000

 '
au.cor = getCov(lower, names = c("sa", "rt", "bp","imp", "ao", "we"))
au.cor

au.cov = cor2cov(R = au.cor, sds = c(0.629, 0.341, 0.560, 
                                         0.318,0.284, 0.291 ))
au.cov


model = '
	 	   auf =~ sa + rt + bp + imp
 	 '
#summary(onefactor)
results = sem(model, sample.cov=au.cov, sample.nobs=605)
summary(results, standardize=TRUE, fit.measures=TRUE)
modificationIndices(results, minimum.value = 0)

library(semPlot)

semPaths(results,
         whatLabels = "std",
         layout = "tree",
         style = "ram",
         rotation = 1,
         sizeMan = 7,
         sizeLat = 7,
         color = "lightgray",
         edge.label.cex = 1.2,
         label.cex = 1.3)

```




# Structural Equation Model

Reading assignment : Kulophas, D., Hallinger, P., Ruengtrakul, A., & Wongwanich, S. (2018). Exploring the effects of authentic leadership on academic optimism and teacher engagement in Thailand. International Journal of Educational Management, 32(1), 27-45. https://doi.org/10.1108/IJEM-10-2016-0233

- Data in SPSS format [Download](https://github.com/trsamp/SEM101/blob/main/data/03SEM.sav)

```{r}
library(lavaan)

lower = '
1.000 
0.859 1.000 
0.873 0.882 1.000
0.816 0.854 0.852 1.000
0.281 0.319 0.297 0.301 1.000
0.369 0.363 0.343 0.363 0.628 1.000

 '
au.cor = getCov(lower, names = c("sa", "rt", "bp","imp", "ao", "we"))
au.cor

au.cov = cor2cov(R = au.cor, sds = c(0.629, 0.341, 0.560, 
                                         0.318,0.284, 0.291 ))
au.cov


model = '
	 	   auf =~ sa + rt + bp + imp
	     aof =~ ao
	     wef =~ we
	     wef~ aof + auf
	     aof ~ auf
	     ao ~~ .01*ao
	     we ~~ .01*we
	     sa ~~ bp
 	 '
#summary(onefactor)
results = sem(model, sample.cov=au.cov, sample.nobs=605)
summary(results, standardize=TRUE, fit.measures=TRUE)
modificationIndices(results, minimum.value = 0)

library(semPlot)

semPaths(results,
         whatLabels = "std",
         layout = "tree")

sessionInfo()

```

# Growth modeling

```{r}
library(lavaan)

GW <- read.csv("D:/OneDrive/00Recent Draft/HAI64/Rgrowth/Zgrowth.csv", header = TRUE)

```
```{r}
m1 <-   'i =~ 1*HAI61 + 1*HAI62 + 1*HAI63 + 1*HAI64
         s =~ 0*HAI61+ 1*HAI62 + 2*HAI63 + 3*HAI64
          HAI61 ~ ONET61
          HAI62 ~ ONET62
          HAI63 ~ ONET63
          HAI64 ~ ONET64
          i ~ A4.2
          s ~ A4.2
'
fit_m1 <- growth(m1, data= GW)
summary(fit_m1, rsquare = TRUE, standardize = TRUE)

fitMeasures(fit_m1, c("cfi","tli", "rmsea","srmr"))

#latent correlation
lavInspect(fit_m1, "cor.lv")

?lavInspect

library(semPlot)

semPaths(fit_m1,
         whatLabels = "std",
         layout = "tree")
```












