---
title: "SEM with Lavaan"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 1
    #code_folding: hide
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```
```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
```


Last compiled: `r Sys.Date()`


# Path analysis

Reading assignment : Kurt, T., Duyar, I., & Calik, T. (2012). Are we legitimate yet? A closer look at the casual relationship mechanisms among principal leadership, teacher self‐efficacy and collective efficacy. Journal of Management Development, 31, 71-86. 

- Data in .txt format [Download](https://github.com/trsamp/SEM101/blob/main/data/01PA.txt)
- Data in SPSS format [Download](https://github.com/trsamp/SEM101/blob/main/data/01PA.sav)

```

TITLE: individual montecarlo
DATA:
  FILE IS data2.txt; !keep all file in the same folder

VARIABLE:
  NAMES ARE TFL TSL CTE TEF; !all variable in "data2.txt"
  USEVARIABLES ARE TFL TSL CTE TEF; 

MODEL: !put the syntax indicate causal relationships
	TEF ON CTE TSL TFL; ! TEF is regressed on CTE TSL TEL;
	CTE ON TSL TFL;
   TSL with TFL;

MODEL INDIRECT:
TEF IND TFL;

OUTPUT: SAMPSTAT STDYX; !standardized coefficient need to be report

```

# Confirmatory Factor Analysis

Reading assignment : Kulophas, D., Hallinger, P., Ruengtrakul, A., & Wongwanich, S. (2018). Exploring the effects of authentic leadership on academic optimism and teacher engagement in Thailand. International Journal of Educational Management, 32(1), 27-45. https://doi.org/10.1108/IJEM-10-2016-0233

- Data in SPSS format [Download](https://github.com/trsamp/SEM101/blob/main/data/03SEM.sav)

```{r}
library(lavaan)

lower = '
1.000 
0.859 1.000 
0.873 0.882 1.000
0.816 0.854 0.852 1.000
0.281 0.319 0.297 0.301 1.000
0.369 0.363 0.343 0.363 0.628 1.000

 '
au.cor = getCov(lower, names = c("sa", "rt", "bp","imp", "ao", "we"))
au.cor

au.cov = cor2cov(R = au.cor, sds = c(0.629, 0.341, 0.560, 
                                         0.318,0.284, 0.291 ))
au.cov


model = '
	 	   auf =~ sa + rt + bp + imp
 	 '
#summary(onefactor)
results = sem(model, sample.cov=au.cov, sample.nobs=605)
summary(results, standardize=TRUE, fit.measures=TRUE)
modificationIndices(results, minimum.value = 0)

library(semPlot)

semPaths(results,
         whatLabels = "std",
         layout = "tree",
         style = "ram",
         rotation = 1,
         sizeMan = 7,
         sizeLat = 7,
         color = "lightgray",
         edge.label.cex = 1.2,
         label.cex = 1.3)

```




# Structural Equation Model

Reading assignment : Kulophas, D., Hallinger, P., Ruengtrakul, A., & Wongwanich, S. (2018). Exploring the effects of authentic leadership on academic optimism and teacher engagement in Thailand. International Journal of Educational Management, 32(1), 27-45. https://doi.org/10.1108/IJEM-10-2016-0233

- Data in SPSS format [Download](https://github.com/trsamp/SEM101/blob/main/data/03SEM.sav)

```{r}
library(lavaan)

lower = '
1.000 
0.859 1.000 
0.873 0.882 1.000
0.816 0.854 0.852 1.000
0.281 0.319 0.297 0.301 1.000
0.369 0.363 0.343 0.363 0.628 1.000

 '
au.cor = getCov(lower, names = c("sa", "rt", "bp","imp", "ao", "we"))
au.cor

au.cov = cor2cov(R = au.cor, sds = c(0.629, 0.341, 0.560, 
                                         0.318,0.284, 0.291 ))
au.cov


model = '
	 	   auf =~ sa + rt + bp + imp
	     aof =~ ao
	     wef =~ we
	     wef~ aof + auf
	     aof ~ auf
	     ao ~~ .01*ao
	     we ~~ .01*we
	     sa ~~ bp
 	 '
#summary(onefactor)
results = sem(model, sample.cov=au.cov, sample.nobs=605)
summary(results, standardize=TRUE, fit.measures=TRUE)
modificationIndices(results, minimum.value = 0)

library(semPlot)

semPaths(results,
         whatLabels = "std",
         layout = "tree")

sessionInfo()

```