---
title: "SEM with Mplus"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    toc_depth: 5
    #code_folding: hide
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
```


Last compiled: `r Sys.Date()`


## 1.Path analysis

Reading assignment : Kurt, T., Duyar, I., & Calik, T. (2012). Are we legitimate yet? A closer look at the casual relationship mechanisms among principal leadership, teacher self‐efficacy and collective efficacy. Journal of Management Development, 31, 71-86. 

- Data in .txt format [Download](https://github.com/trsamp/SEM101/blob/main/data/01PA.txt)
- Data in SPSS format [Download](https://github.com/trsamp/SEM101/blob/main/data/01PA.sav)

```

TITLE: path analysis
DATA:
  FILE IS data2.txt; !keep all file in the same folder

VARIABLE:
  NAMES ARE TFL TSL CTE TEF; !all variable in "data2.txt"
  USEVARIABLES ARE TFL TSL CTE TEF; 

MODEL: !put the syntax indicate causal relationships
	TEF ON CTE TSL TFL; ! TEF is regressed on CTE TSL TEL;
	CTE ON TSL TFL;
   TSL with TFL;

MODEL INDIRECT:
TEF IND TFL;

OUTPUT: SAMPSTAT STDYX; 

```
#### PRINTOUT

```
INPUT READING TERMINATED NORMALLY



path analysis

SUMMARY OF ANALYSIS

Number of groups                                                 1
Number of observations                                         810

Number of dependent variables                                    2
Number of independent variables                                  2
Number of continuous latent variables                            0

Observed dependent variables

  Continuous
   CTE         TEF

Observed independent variables
   TFL         TSL


Estimator                                                       ML
Information matrix                                        OBSERVED
Maximum number of iterations                                  1000
Convergence criterion                                    0.500D-04
Maximum number of steepest descent iterations                   20

Input data file(s)
  data2.txt

Input data format  FREE


SAMPLE STATISTICS


     SAMPLE STATISTICS


           Means
              CTE           TEF           TFL           TSL
              ________      ________      ________      ________
                4.310         6.920         2.660         1.890


           Covariances
              CTE           TEF           TFL           TSL
              ________      ________      ________      ________
 CTE            0.422
 TEF            0.276         0.979
 TFL            0.181         0.186         0.672
 TSL           -0.050        -0.016         0.063         0.302


           Correlations
              CTE           TEF           TFL           TSL
              ________      ________      ________      ________
 CTE            1.000
 TEF            0.430         1.000
 TFL            0.340         0.230         1.000
 TSL           -0.140        -0.030         0.140         1.000


UNIVARIATE SAMPLE STATISTICS


     UNIVARIATE HIGHER-ORDER MOMENT DESCRIPTIVE STATISTICS

         Variable/         Mean/     Skewness/   Minimum/ % with                Percentiles
        Sample Size      Variance    Kurtosis    Maximum  Min/Max      20%/60%    40%/80%    Median

     CTE                   4.310       0.063       2.215    0.12%       3.781      4.160      4.304
             810.000       0.422      -0.029       6.519    0.12%       4.450      4.831
     TEF                   6.920      -0.117       4.006    0.12%       6.077      6.727      6.946
             810.000       0.979      -0.091       9.771    0.12%       7.192      7.741
     TFL                   2.660       0.075      -0.084    0.12%       1.974      2.399      2.661
             810.000       0.672      -0.009       5.094    0.12%       2.882      3.353
     TSL                   1.890       0.091       0.062    0.12%       1.405      1.749      1.887
             810.000       0.302      -0.089       3.571    0.12%       2.015      2.341


THE MODEL ESTIMATION TERMINATED NORMALLY



MODEL FIT INFORMATION

Number of Free Parameters                       14

Loglikelihood

          H0 Value                       -3431.893
          H1 Value                       -3431.893

Information Criteria

          Akaike (AIC)                    6891.787
          Bayesian (BIC)                  6957.545
          Sample-Size Adjusted BIC        6913.087
            (n* = (n + 2) / 24)

Chi-Square Test of Model Fit

          Value                              0.000
          Degrees of Freedom                     0
          P-Value                           0.0000

RMSEA (Root Mean Square Error Of Approximation)

          Estimate                           0.000
          90 Percent C.I.                    0.000  0.000
          Probability RMSEA <= .05           0.000

CFI/TLI

          CFI                                1.000
          TLI                                1.000

Chi-Square Test of Model Fit for the Baseline Model

          Value                            306.763
          Degrees of Freedom                     5
          P-Value                           0.0000

SRMR (Standardized Root Mean Square Residual)

          Value                              0.000



MODEL RESULTS

                                                    Two-Tailed
                    Estimate       S.E.  Est./S.E.    P-Value

 TEF      ON
    CTE                0.610      0.052     11.690      0.000
    TSL                0.024      0.059      0.406      0.685
    TFL                0.111      0.041      2.683      0.007

 CTE      ON
    TSL               -0.226      0.039     -5.854      0.000
    TFL                0.291      0.026     11.221      0.000

 TSL      WITH
    TFL                0.063      0.016      3.946      0.000

 Means
    TFL                2.660      0.029     92.380      0.000
    TSL                1.890      0.019     97.861      0.000

 Intercepts
    CTE                3.964      0.095     41.522      0.000
    TEF                3.950      0.251     15.749      0.000

 Variances
    TFL                0.672      0.033     20.125      0.000
    TSL                0.302      0.015     20.125      0.000

 Residual Variances
    CTE                0.358      0.018     20.125      0.000
    TEF                0.790      0.039     20.125      0.000


STANDARDIZED MODEL RESULTS


STDYX Standardization

                                                    Two-Tailed
                    Estimate       S.E.  Est./S.E.    P-Value

 TEF      ON
    CTE                0.401      0.032     12.568      0.000
    TSL                0.013      0.033      0.406      0.685
    TFL                0.092      0.034      2.691      0.007

 CTE      ON
    TSL               -0.191      0.032     -5.945      0.000
    TFL                0.367      0.031     12.005      0.000

 TSL      WITH
    TFL                0.140      0.034      4.064      0.000

 Means
    TFL                3.246      0.088     36.899      0.000
    TSL                3.438      0.092     37.224      0.000

 Intercepts
    CTE                6.102      0.227     26.918      0.000
    TEF                3.993      0.313     12.755      0.000

 Variances
    TFL                1.000      0.000    999.000    999.000
    TSL                1.000      0.000    999.000    999.000

 Residual Variances
    CTE                0.849      0.023     36.561      0.000
    TEF                0.807      0.025     32.391      0.000


R-SQUARE

    Observed                                        Two-Tailed
    Variable        Estimate       S.E.  Est./S.E.    P-Value

    CTE                0.151      0.023      6.528      0.000
    TEF                0.193      0.025      7.747      0.000

QUALITY OF NUMERICAL RESULTS

     Condition Number for the Information Matrix              0.152E-02
       (ratio of smallest to largest eigenvalue)


TOTAL, TOTAL INDIRECT, SPECIFIC INDIRECT, AND DIRECT EFFECTS


                                                    Two-Tailed
                    Estimate       S.E.  Est./S.E.    P-Value

Effects from TFL to TEF

  Total                0.288      0.042      6.932      0.000
  Total indirect       0.177      0.022      8.095      0.000

  Specific indirect

    TEF
    CTE
    TFL                0.177      0.022      8.095      0.000

  Direct
    TEF
    TFL                0.111      0.041      2.683      0.007



STANDARDIZED TOTAL, TOTAL INDIRECT, SPECIFIC INDIRECT, AND DIRECT EFFECTS


STDYX Standardization

                                                    Two-Tailed
                    Estimate       S.E.  Est./S.E.    P-Value

Effects from TFL to TEF

  Total                0.239      0.033      7.133      0.000
  Total indirect       0.147      0.017      8.485      0.000

  Specific indirect

    TEF
    CTE
    TFL                0.147      0.017      8.485      0.000

  Direct
    TEF
    TFL                0.092      0.034      2.691      0.007
```

#### DIAGRAM : Path Analysis
</div>
<div class="col-sm-10">
<a href = "https://crumplab.github.io">
[](images/PA.png)



## 2.Confirmatory Factor Analysis

Reading assignment : Kulophas, D., Hallinger, P., Ruengtrakul, A., & Wongwanich, S. (2018). Exploring the effects of authentic leadership on academic optimism and teacher engagement in Thailand. International Journal of Educational Management, 32(1), 27-45. https://doi.org/10.1108/IJEM-10-2016-0233

- Data in SPSS format [Download](https://github.com/trsamp/SEM101/blob/main/data/03SEM.sav)

```
TITLE:  CFA model

DATA:
  FILE IS data_al.txt;
  TYPE IS CORRELATION MEANS STD; 
  NOBSERVATIONS = 605; 
VARIABLE:
  NAMES ARE SA RT BP IMP AO WE;
  USEVARIABLES ARE SA RT BP IMP ;

MODEL:
  AL BY SA RT BP IMP;

OUTPUT:  SAMPSTAT STDYX Mod TECH4;
```
#### Printout

```
CFA model

SUMMARY OF ANALYSIS

Number of groups                                                 1
Number of observations                                         605

Number of dependent variables                                    4
Number of independent variables                                  0
Number of continuous latent variables                            1

Observed dependent variables

  Continuous
   SA          RT          BP          IMP

Continuous latent variables
   AL


Estimator                                                       ML
Information matrix                                        EXPECTED
Maximum number of iterations                                  1000
Convergence criterion                                    0.500D-04
Maximum number of steepest descent iterations                   20

Input data file(s)
  data_al.txt

Input data format  FREE


SAMPLE STATISTICS


     SAMPLE STATISTICS


           Means/Intercepts/Thresholds
              SA            RT            BP            IMP
              ________      ________      ________      ________
                2.708         1.543         2.373         1.473


           Covariances/Correlations/Residual Correlations
              SA            RT            BP            IMP
              ________      ________      ________      ________
 SA             0.396
 RT             0.184         0.116
 BP             0.308         0.168         0.314
 IMP            0.163         0.093         0.152         0.101


THE MODEL ESTIMATION TERMINATED NORMALLY



MODEL FIT INFORMATION

Number of Free Parameters                       12

Loglikelihood

          H0 Value                         -65.721
          H1 Value                         -62.423

Information Criteria

          Akaike (AIC)                     155.443
          Bayesian (BIC)                   208.305
          Sample-Size Adjusted BIC         170.208
            (n* = (n + 2) / 24)

Chi-Square Test of Model Fit

          Value                              6.596
          Degrees of Freedom                     2
          P-Value                           0.0370

RMSEA (Root Mean Square Error Of Approximation)

          Estimate                           0.062
          90 Percent C.I.                    0.013  0.117
          Probability RMSEA <= .05           0.280

CFI/TLI

          CFI                                0.998
          TLI                                0.995

Chi-Square Test of Model Fit for the Baseline Model

          Value                           2788.139
          Degrees of Freedom                     6
          P-Value                           0.0000

SRMR (Standardized Root Mean Square Residual)

          Value                              0.004



MODEL RESULTS

                                                    Two-Tailed
                    Estimate       S.E.  Est./S.E.    P-Value

 AL       BY
    SA                 1.000      0.000    999.000    999.000
    RT                 0.554      0.013     41.403      0.000
    BP                 0.918      0.022     42.514      0.000
    IMP                0.497      0.014     36.824      0.000

 Intercepts
    SA                 2.708      0.026    105.983      0.000
    RT                 1.543      0.014    111.391      0.000
    BP                 2.373      0.023    104.315      0.000
    IMP                1.473      0.013    114.028      0.000

 Variances
    AL                 0.332      0.023     14.687      0.000

 Residual Variances
    SA                 0.063      0.005     13.595      0.000
    RT                 0.014      0.001     12.085      0.000
    BP                 0.033      0.003     11.259      0.000
    IMP                0.019      0.001     14.283      0.000


STANDARDIZED MODEL RESULTS


STDYX Standardization

                                                    Two-Tailed
                    Estimate       S.E.  Est./S.E.    P-Value

 AL       BY
    SA                 0.917      0.008    120.416      0.000
    RT                 0.938      0.006    150.146      0.000
    BP                 0.945      0.006    164.281      0.000
    IMP                0.902      0.009    104.260      0.000

 Intercepts
    SA                 4.309      0.130     33.050      0.000
    RT                 4.529      0.136     33.204      0.000
    BP                 4.241      0.129     32.999      0.000
    IMP                4.636      0.139     33.271      0.000

 Variances
    AL                 1.000      0.000    999.000    999.000

 Residual Variances
    SA                 0.159      0.014     11.424      0.000
    RT                 0.121      0.012     10.340      0.000
    BP                 0.106      0.011      9.763      0.000
    IMP                0.187      0.016     11.976      0.000


R-SQUARE

    Observed                                        Two-Tailed
    Variable        Estimate       S.E.  Est./S.E.    P-Value

    SA                 0.841      0.014     60.208      0.000
    RT                 0.879      0.012     75.073      0.000
    BP                 0.894      0.011     82.140      0.000
    IMP                0.813      0.016     52.130      0.000


QUALITY OF NUMERICAL RESULTS

     Condition Number for the Information Matrix              0.125E-02
       (ratio of smallest to largest eigenvalue)


MODEL MODIFICATION INDICES

NOTE:  Modification indices for direct effects of observed dependent variables
regressed on covariates may not be included.  To include these, request
MODINDICES (ALL).

Minimum M.I. value for printing the modification index    10.000

                                   M.I.     E.P.C.  Std E.P.C.  StdYX E.P.C.

No modification indices above the minimum value.



TECHNICAL 4 OUTPUT


     ESTIMATES DERIVED FROM THE MODEL


           ESTIMATED MEANS FOR THE LATENT VARIABLES
              AL
              ________
                0.000


           ESTIMATED COVARIANCE MATRIX FOR THE LATENT VARIABLES
              AL
              ________
 AL             0.332


           ESTIMATED CORRELATION MATRIX FOR THE LATENT VARIABLES
              AL
              ________
 AL             1.000


     ESTIMATES DERIVED FROM THE MODEL


           S.E. FOR ESTIMATED MEANS FOR THE LATENT VARIABLES
              AL
              ________
                0.000


           EST./S.E. FOR ESTIMATED MEANS FOR THE LATENT VARIABLES
              AL
              ________
                0.000


           TWO-TAILED P-VALUE FOR ESTIMATED MEANS FOR THE LATENT VARIABLES
              AL
              ________
                1.000


           S.E. FOR ESTIMATED COVARIANCE MATRIX FOR THE LATENT VARIABLES
              AL
              ________
 AL             0.023


           EST./S.E. FOR ESTIMATED COVARIANCE MATRIX FOR THE LATENT VARIABLES
              AL
              ________
 AL            14.687


           TWO-TAILED P-VALUE FOR ESTIMATED COVARIANCE MATRIX FOR THE LATENT VARIABLES
              AL
              ________
 AL             0.000


           S.E. FOR ESTIMATED CORRELATION MATRIX FOR THE LATENT VARIABLES
              AL
              ________
 AL             0.000


           EST./S.E. FOR ESTIMATED CORRELATION MATRIX FOR THE LATENT VARIABLES
              AL
              ________
 AL           999.000


           TWO-TAILED P-VALUE FOR ESTIMATED CORRELATION MATRIX FOR THE LATENT VARIABLES
              AL
              ________
 AL             0.000

```

#### DIAGRAM : CFA
</div>
<div class="col-sm-10">
<a href = "https://crumplab.github.io">
[](images/CFA.png)


## 3.Structural Equation Modeling

Reading assignment : Kulophas, D., Hallinger, P., Ruengtrakul, A., & Wongwanich, S. (2018). Exploring the effects of authentic leadership on academic optimism and teacher engagement in Thailand. International Journal of Educational Management, 32(1), 27-45. https://doi.org/10.1108/IJEM-10-2016-0233

- Data in SPSS format [Download](https://github.com/trsamp/SEM101/blob/main/data/03SEM.sav)

```
TITLE:  authentic leadership model

DATA:
  FILE IS data_al.txt;
  TYPE IS CORRELATION MEANS STD; 
  NOBSERVATIONS = 605; 
VARIABLE:
  NAMES ARE SA RT BP IMP AO WE;
  USEVARIABLES ARE SA RT BP IMP AO WE;

MODEL:
  AL BY SA RT BP IMP;
  fAO BY AO;  AO@.005;
  fWE BY WE;  WE@.011;
  fWE ON fAO AL;
  fAO ON AL;
  BP WITH SA;
 
 MODEL indirect:
 fWE IND AL;
  OUTPUT:  SAMPSTAT STDYX Mod TECH4;
```
#### PRINTOUT

```
authentic leadership model

SUMMARY OF ANALYSIS

Number of groups                                                 1
Number of observations                                         605

Number of dependent variables                                    6
Number of independent variables                                  0
Number of continuous latent variables                            3

Observed dependent variables

  Continuous
   SA          RT          BP          IMP         AO          WE

Continuous latent variables
   AL          FAO         FWE


Estimator                                                       ML
Information matrix                                        EXPECTED
Maximum number of iterations                                  1000
Convergence criterion                                    0.500D-04
Maximum number of steepest descent iterations                   20

Input data file(s)
  data_al.txt

Input data format  FREE


SAMPLE STATISTICS


     SAMPLE STATISTICS


           Means/Intercepts/Thresholds
              SA            RT            BP            IMP           AO
              ________      ________      ________      ________      ________
                2.708         1.543         2.373         1.473         3.024


           Means/Intercepts/Thresholds
              WE
              ________
                2.588


           Covariances/Correlations/Residual Correlations
              SA            RT            BP            IMP           AO
              ________      ________      ________      ________      ________
 SA             0.396
 RT             0.184         0.116
 BP             0.308         0.168         0.314
 IMP            0.163         0.093         0.152         0.101
 AO             0.050         0.031         0.047         0.027         0.081
 WE             0.068         0.036         0.056         0.034         0.052


           Covariances/Correlations/Residual Correlations
              WE
              ________
 WE             0.085


THE MODEL ESTIMATION TERMINATED NORMALLY



MODEL FIT INFORMATION

Number of Free Parameters                       20

Loglikelihood

          H0 Value                         -68.414
          H1 Value                         -62.254

Information Criteria

          Akaike (AIC)                     176.827
          Bayesian (BIC)                   264.932
          Sample-Size Adjusted BIC         201.437
            (n* = (n + 2) / 24)

Chi-Square Test of Model Fit

          Value                             12.320
          Degrees of Freedom                     7
          P-Value                           0.0905

RMSEA (Root Mean Square Error Of Approximation)

          Estimate                           0.035
          90 Percent C.I.                    0.000  0.067
          Probability RMSEA <= .05           0.739

CFI/TLI

          CFI                                0.998
          TLI                                0.996

Chi-Square Test of Model Fit for the Baseline Model

          Value                           3203.520
          Degrees of Freedom                    15
          P-Value                           0.0000

SRMR (Standardized Root Mean Square Residual)

          Value                              0.007



MODEL RESULTS

                                                    Two-Tailed
                    Estimate       S.E.  Est./S.E.    P-Value

 AL       BY
    SA                 1.000      0.000    999.000    999.000
    RT                 0.564      0.014     39.206      0.000
    BP                 0.919      0.021     43.243      0.000
    IMP                0.505      0.014     35.483      0.000

 FAO      BY
    AO                 1.000      0.000    999.000    999.000

 FWE      BY
    WE                 1.000      0.000    999.000    999.000

 FWE      ON
    FAO                0.619      0.036     17.203      0.000
    AL                 0.097      0.017      5.613      0.000

 FAO      ON
    AL                 0.162      0.020      8.200      0.000

 BP       WITH
    SA                 0.008      0.004      2.283      0.022

 Intercepts
    SA                 2.708      0.026    105.983      0.000
    RT                 1.543      0.014    111.391      0.000
    BP                 2.373      0.023    104.315      0.000
    IMP                1.473      0.013    114.028      0.000
    AO                 3.024      0.012    262.120      0.000
    WE                 2.588      0.012    218.931      0.000

 Variances
    AL                 0.325      0.023     14.309      0.000

 Residual Variances
    SA                 0.070      0.006     12.233      0.000
    RT                 0.013      0.001     10.154      0.000
    BP                 0.039      0.004     10.400      0.000
    IMP                0.018      0.001     13.648      0.000
    AO                 0.005      0.000    999.000    999.000
    WE                 0.011      0.000    999.000    999.000
    FAO                0.067      0.004     16.100      0.000
    FWE                0.035      0.003     12.699      0.000


STANDARDIZED MODEL RESULTS


STDYX Standardization

                                                    Two-Tailed
                    Estimate       S.E.  Est./S.E.    P-Value

 AL       BY
    SA                 0.907      0.009     99.014      0.000
    RT                 0.944      0.006    146.712      0.000
    BP                 0.936      0.007    130.828      0.000
    IMP                0.906      0.009    105.787      0.000

 FAO      BY
    AO                 0.968      0.002    525.412      0.000

 FWE      BY
    WE                 0.933      0.004    232.557      0.000

 FWE      ON
    FAO                0.627      0.030     20.874      0.000
    AL                 0.203      0.036      5.689      0.000

 FAO      ON
    AL                 0.337      0.038      8.805      0.000

 BP       WITH
    SA                 0.161      0.062      2.585      0.010

 Intercepts
    SA                 4.309      0.130     33.050      0.000
    RT                 4.529      0.136     33.204      0.000
    BP                 4.241      0.129     32.999      0.000
    IMP                4.636      0.139     33.271      0.000
    AO                10.657      0.309     34.483      0.000
    WE                 8.901      0.259     34.354      0.000

 Variances
    AL                 1.000      0.000    999.000    999.000

 Residual Variances
    SA                 0.177      0.017     10.649      0.000
    RT                 0.110      0.012      9.024      0.000
    BP                 0.124      0.013      9.231      0.000
    IMP                0.179      0.016     11.556      0.000
    AO                 0.062      0.004     17.393      0.000
    WE                 0.130      0.007     17.393      0.000
    FAO                0.886      0.026     34.353      0.000
    FWE                0.480      0.034     13.990      0.000


R-SQUARE

    Observed                                        Two-Tailed
    Variable        Estimate       S.E.  Est./S.E.    P-Value

    SA                 0.823      0.017     49.507      0.000
    RT                 0.890      0.012     73.356      0.000
    BP                 0.876      0.013     65.414      0.000
    IMP                0.821      0.016     52.893      0.000
    AO                 0.938      0.004    262.706      0.000
    WE                 0.870      0.007    116.279      0.000

     Latent                                         Two-Tailed
    Variable        Estimate       S.E.  Est./S.E.    P-Value

    FAO                0.114      0.026      4.402      0.000
    FWE                0.520      0.034     15.154      0.000


QUALITY OF NUMERICAL RESULTS

     Condition Number for the Information Matrix              0.871E-03
       (ratio of smallest to largest eigenvalue)


TOTAL, TOTAL INDIRECT, SPECIFIC INDIRECT, AND DIRECT EFFECTS


                                                    Two-Tailed
                    Estimate       S.E.  Est./S.E.    P-Value

Effects from AL to FWE

  Total                0.197      0.020      9.888      0.000
  Total indirect       0.100      0.014      7.431      0.000

  Specific indirect

    FWE
    FAO
    AL                 0.100      0.014      7.431      0.000

  Direct
    FWE
    AL                 0.097      0.017      5.613      0.000



STANDARDIZED TOTAL, TOTAL INDIRECT, SPECIFIC INDIRECT, AND DIRECT EFFECTS


STDYX Standardization

                                                    Two-Tailed
                    Estimate       S.E.  Est./S.E.    P-Value

Effects from AL to FWE

  Total                0.414      0.038     11.025      0.000
  Total indirect       0.211      0.026      8.164      0.000

  Specific indirect

    FWE
    FAO
    AL                 0.211      0.026      8.164      0.000

  Direct
    FWE
    AL                 0.203      0.036      5.689      0.000




MODEL MODIFICATION INDICES

NOTE:  Modification indices for direct effects of observed dependent variables
regressed on covariates may not be included.  To include these, request
MODINDICES (ALL).

Minimum M.I. value for printing the modification index    10.000

                                   M.I.     E.P.C.  Std E.P.C.  StdYX E.P.C.

No modification indices above the minimum value.



TECHNICAL 4 OUTPUT


     ESTIMATES DERIVED FROM THE MODEL


           ESTIMATED MEANS FOR THE LATENT VARIABLES
              AL            FAO           FWE
              ________      ________      ________
                0.000         0.000         0.000


           ESTIMATED COVARIANCE MATRIX FOR THE LATENT VARIABLES
              AL            FAO           FWE
              ________      ________      ________
 AL             0.325
 FAO            0.053         0.076
 FWE            0.064         0.052         0.074


           ESTIMATED CORRELATION MATRIX FOR THE LATENT VARIABLES
              AL            FAO           FWE
              ________      ________      ________
 AL             1.000
 FAO            0.337         1.000
 FWE            0.414         0.695         1.000


     ESTIMATES DERIVED FROM THE MODEL


           S.E. FOR ESTIMATED MEANS FOR THE LATENT VARIABLES
              AL            FAO           FWE
              ________      ________      ________
                0.000         0.000         0.000


           EST./S.E. FOR ESTIMATED MEANS FOR THE LATENT VARIABLES
              AL            FAO           FWE
              ________      ________      ________
                0.000         0.000         0.000


           TWO-TAILED P-VALUE FOR ESTIMATED MEANS FOR THE LATENT VARIABLES
              AL            FAO           FWE
              ________      ________      ________
                1.000         1.000         1.000


           S.E. FOR ESTIMATED COVARIANCE MATRIX FOR THE LATENT VARIABLES
              AL            FAO           FWE
              ________      ________      ________
 AL             0.023
 FAO            0.007         0.005
 FWE            0.007         0.004         0.005


           EST./S.E. FOR ESTIMATED COVARIANCE MATRIX FOR THE LATENT VARIABLES
              AL            FAO           FWE
              ________      ________      ________
 AL            14.309
 FAO            7.420        16.313
 FWE            8.601        13.081        15.130


           TWO-TAILED P-VALUE FOR ESTIMATED COVARIANCE MATRIX FOR THE LATENT VARIABLES
              AL            FAO           FWE
              ________      ________      ________
 AL             0.000
 FAO            0.000         0.000
 FWE            0.000         0.000         0.000


           S.E. FOR ESTIMATED CORRELATION MATRIX FOR THE LATENT VARIABLES
              AL            FAO           FWE
              ________      ________      ________
 AL             0.000
 FAO            0.038         0.000
 FWE            0.038         0.026         0.000


           EST./S.E. FOR ESTIMATED CORRELATION MATRIX FOR THE LATENT VARIABLES
              AL            FAO           FWE
              ________      ________      ________
 AL           999.000
 FAO            8.805       999.000
 FWE           11.025        27.219       999.000


           TWO-TAILED P-VALUE FOR ESTIMATED CORRELATION MATRIX FOR THE LATENT VARIABLES
              AL            FAO           FWE
              ________      ________      ________
 AL             0.000
 FAO            0.000         0.000
 FWE            0.000         0.000         0.000

```


#### DIAGRAM : SEM
</div>
<div class="col-sm-10">
<a href = "https://crumplab.github.io">
[](images/CFA.png)